Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-03-26 ms.tex
test push
test commit
changes for ref's comments

Early research into GW emission from CCSNe focused on the bounce and early post bounce phase of the explosion in rotating progenitors.
These investigations found that increasing the angular momentum of the core leads to a larger strain peak at bounce \citep{muller:1982,moench:1991,yamada:1995,zwerger:1997,dimm:2002,kotake:2003,shibata:2004}.  
More recent investigations of rotating core collapse examine the role of the angular momentum distribution within the supernova progenitor and find it only important in the rapid rotation regime, where the ratio of kinetic to gravitational potential energy ($T/|W|$) $ \gtrsim 8\%$ at bounce \citep{abdik:2014}. In order to examine GW emission at later times, different groups have considered other factors for nonrotating cases---for example, convection in the post shock region \citep{burrows:1996,muller:1997,muller:2004,murphy:2009,marek:2009b}, the standing accretion shock instability (SASI) \citep{blondin:2003,blondin:2006,ohnishi:2006,foglizzo:2007,scheck:2008,iwakami:2009,fernandez:2010}\textcolor{red}{[9], and protoneutron star (PNS) vibrational modes \citep{cerda-duran:2013,torres-forne:2018,torres-forne:2019}}.  \citet{moro:2018} investigate GW emission for moderate rotational speeds ($\Omega_{\mathrm{core}} = 0.2$ rad s$^{-1}$) for a single progenitor mass ($13 M_\odot$) over one second post bounce.  \citet{pan:2018}, \citet{kuroda:2018}, \textcolor{red}{[3]}\citet{cerda-duran:2013}, and \citet{ott:2011} investigate the relationship between black hole formation and GW emission, for a nonrotating 40 $M_\odot$, nonrotating  70 $M_\odot$, a rotating 35 $M_\odot$, and a rotating 75 $M_\odot$ progenitor, respectively.  These works also find stronger GW emission at bounce with increased progenitor angular momentum and loud GW emission at later times for nonrotating CCSNe.

@@

Our results in the previous section support the efficacy of our effective GR potential for accurately modeling the GW signals from CCSNe \textcolor{red}{[8]during the bounce and early post bounce phase.  While the effective GR potential has been shown to underestimate peak frequency from GWs compared to GR, it accurately captures the GW amplitude and PNS compactness during the accretion phase \citep{muller:2013}.  Thus, we now turn to exploring the rotational effects on the GW signal during the accretion phase, up to 300 ms after bounce.}

>>>>

Early research into GW emission from CCSNe focused on the bounce and early post bounce phase of the explosion in rotating progenitors.
These investigations found that increasing the angular momentum of the core leads to a larger strain peak at bounce \citep{muller:1982,moench:1991,yamada:1995,zwerger:1997,dimm:2002,kotake:2003,shibata:2004}.  
More recent investigations of rotating core collapse examine the role of the angular momentum distribution within the supernova progenitor and find it only important in the rapid rotation regime, where the ratio of kinetic to gravitational potential energy ($T/|W|$) $ \gtrsim 8\%$ at bounce \citep{abdik:2014}. In order to examine GW emission at later times, different groups have considered other factors for nonrotating cases---for example, convection in the post shock region \citep{burrows:1996,muller:1997,muller:2004,murphy:2009,marek:2009b}, the standing accretion shock instability (SASI) \citep{blondin:2003,blondin:2006,ohnishi:2006,foglizzo:2007,scheck:2008,iwakami:2009,fernandez:2010}\textcolor{red}{[9], and protoneutron star (PNS) vibrational modes \citep{cerda-duran:2013,torres-forne:2018,torres-forne:2019}}.  \citet{moro:2018} investigate GW emission for moderate rotational speeds ($\Omega_{\mathrm{core}} = 0.2$ rad s$^{-1}$) for a single progenitor mass ($13 M_\odot$) over one second post bounce.  \citet{pan:2018}, \citet{kuroda:2018}, \textcolor{red}{[3]}\citet{cerda-duran:2013}, and \citet{ott:2011} investigate the relationship between black hole formation and GW emission, for a nonrotating 40 $M_\odot$, nonrotating  70 $M_\odot$, \textcolor{red}{[3] a rotating 35 $M_\odot$,} and a rotating 75 $M_\odot$ progenitor, respectively.  These works also find stronger GW emission at bounce with increased progenitor angular momentum and loud GW emission at later times for nonrotating CCSNe.

@@

Our results in the previous section support the efficacy of our effective GR potential for accurately modeling the GW signals from CCSNe. \textcolor{red}{[8]  While the effective GR potential has been shown to underestimate peak frequency from GWs compared to GR, it produces similar GW amplitudes and accurately captures PNS compactness during the accretion phase \citep{muller:2013}.}  Thus, we now turn to exploring the rotational effects on the GW signal during the accretion phase, up to 300 ms after bounce.
